%-------------------------
% Resume - Tran Manh Tuong (Rewritten & Reformatted)
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Accent color
\definecolor{accent}{RGB}{30, 80, 160}

% Section formatting — thinner rule, accent color
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large\bfseries\color{accent}
}{}{0em}{}[\color{accent}\titlerule\vspace{-4pt}]

\pdfgentounicode=1

% ── Custom commands ──────────────────────────────────────────
\newcommand{\resumeItem}[1]{
  \item\small{{#1\vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \small #2 \\
      \textit{\small\color{accent} #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\projectTag}[1]{%
  \vspace{4pt}
  {\small\textbf{\color{accent}#1}}%
  \vspace{-4pt}
}

\newcommand{\techStack}[1]{%
  \vspace{1pt}
  {\small\textit{Tech stack: #1}}%
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{%
  \begin{itemize}[leftmargin=0.22in, topsep=2pt, parsep=0pt, partopsep=0pt, itemsep=2pt]%
}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

% Project sub-block
\newenvironment{projectBlock}[2]{%
  \vspace{-4pt}
  \begin{itemize}[leftmargin=0.22in, label={}, topsep=0pt, parsep=0pt, itemsep=0pt]
  \item \small\textbf{#1} --- #2
  \begin{itemize}[leftmargin=0.18in, topsep=1pt, parsep=0pt, itemsep=1pt]
}{%
  \end{itemize}
  \end{itemize}
  \vspace{-2pt}
}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge\scshape\textbf{Tran Manh Tuong}} \\ \vspace{5pt}
    {\small\color{accent}\textbf{Backend Developer}} \\ \vspace{5pt}
    \small
    \faPhone\ \href{tel:+84775682978}{+84 77 568 2978}
    \quad\textbar\quad
    \faEnvelope\ \href{mailto:tuongtran1345@gmail.com}{tuongtran1345@gmail.com}
    \quad\textbar\quad
    \faLinkedin\ \href{https://linkedin.com/in/tuong-tm}{LinkedIn}
    \quad\textbar\quad
    \faMapMarker*\ Ho Chi Minh, Vietnam
\end{center}

%-----------SUMMARY-----------
% \section{Professional Summary}
% \begin{itemize}[leftmargin=0.15in, label={}]
%   \small{\item{
%     Backend Developer with 3+ years of experience building secure, high-availability systems in \textbf{banking} and \textbf{fintech}. Hands-on expertise in \textbf{Core Banking} (CASA, Loan Lifecycle), \textbf{digital signature infrastructure} (PKI, XMLDSig, CMS/PKCS\#7), and microservices architecture. Proven ability to deliver complex integrations between Core Banking platforms and external OTT/digital channels.
%   }}
% \end{itemize}

% \section{Summary}
% \begin{itemize}[leftmargin=0.15in, label={}]
%   \small{\item{
%     As a programmer with 3 years of professional experience in Java, SAP, and Core Banking. I have worked on a variety of projects and gained a solid understanding of core banking system, workflows, project execution, and deployment. With a strong commitment to continuous learning and deepening my expertise, I aim to become an even more proficient programmer. I look forward to contributing to and growing with your company in the near future. 
% }}
% \end{itemize}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Banking:}{ Core Banking Systems, CASA, Loan Lifecycle.} \\
     \textbf{SAP:}{ SAP Basis, SAP HANA, ABAP, ChaRM, OSS Management.} \\
     \textbf{Languages/Frameworks:}{ Java (8/11/17), Spring Boot, REST API, PL/SQL, JavaScript.} \\
     \textbf{Cloud/DevOps:}{ Linux, Docker, RabbitMQ, Redis, Consul, Microservices, Asterisk.} \\
     \textbf{Databases:}{ Oracle (Core Banking), PostgreSQL, MySQL, MariaDB.} \\
    %  \textbf{Tools:}{ Git, IntelliJ IDEA, Eclipse, DBeaver, Postman, VSCode.}
    }}
 \end{itemize}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
\resumeSubHeadingListStart

  %--- INDOVINA BANK ---
  \resumeSubheading
    {Indovina Bank}{May 2025 -- Present}
    {IT - SOFTWARE ENGINEER (CORE BANKING)}{Ho Chi Minh, Vietnam}
  \resumeItemListStart
    \resumeItem{Designed and developed RESTful APIs for core banking transactions, ensuring strict data consistency, atomicity, and security compliance.}
    \resumeItem{Developed complex Stored Procedures and automated scheduled jobs for critical operations: account opening, end-of-day settlement, and term deposit auto-renewal.}
    \resumeItem{Built synchronization workflows integrating Core Banking with external OTT digital channels, delivering real-time transaction status updates via REST APIs.}
    \resumeItem{Modeled Core Banking data schemas for CASA and Loan Lifecycle modules, supporting scalable transaction processing at enterprise scale.}
  \resumeItemListEnd

  % \vspace{2pt}
  \begin{projectBlock}{Digital Banking Platform}{Core system for transfers, payments, and account management}
    \resumeItem{Designed and maintained scheduled job workflows to synchronize transactional data between Core Banking and external OTT systems.}
    \resumeItem{Ensured transaction integrity and consistency with real-time REST API notifications.}
    \item \techStack{Java 17, Spring Boot, Oracle DB, PL/SQL, REST API, Docker.}
  \end{projectBlock}

  %--- IDEA PLACE VIETNAM ---
  \resumeSubheading
    {Idea Place Vietnam}{Dec 2023 -- Jan 2025}
    {SAP Consultant}{Ho Chi Minh, Vietnam}
  \resumeItemListStart
    \resumeItem{Collaborated with Japanese clients on daily SAP Basis operations: user management, system monitoring, and issue resolution.}
    \resumeItem{Managed Transport Requests (TRs) and maintained ChaRM statuses across DEV, QA, and PROD landscapes with zero unplanned downtime.}
    \resumeItem{Developed ABAP enhancement packages and produced technical design documents for custom addon programs.}
    \resumeItem{Handled OSS Notes analysis, application, and follow-up to keep SAP systems patched and compliant.}
  \resumeItemListEnd

  %--- LCS GROUP ---
  \resumeSubheading
    {LCS Group}{Oct 2022 -- Oct 2023}
    {Java Developer}{Ho Chi Minh, Vietnam}
  \resumeItemListStart
    \resumeItem{Architected and developed ESign Portal and CRM backend services using Spring Boot and PostgreSQL, serving hundreds of concurrent users.}
    \resumeItem{Implemented PKI infrastructure and digital signature workflows (XMLDSig, CMS/PKCS\#7), including certificate validation and cryptographic operations (AES, RSA).}
    \resumeItem{Integrated RabbitMQ for reliable asynchronous message queuing across microservices; containerized all services with Docker.}
    \resumeItem{Applied Aspect-Oriented Programming (AOP) for cross-cutting concerns: distributed logging, file transfer monitoring, and audit trails.}
  \resumeItemListEnd

  % \vspace{2pt}
  \begin{projectBlock}{ESign Portal (ESP)}{Signature verification services for individuals and enterprises}
    \resumeItem{Implemented AOP-based tracking for data transfer events across the microservices mesh.}
    \resumeItem{Analyzed requirements and optimized the full signature verification pipeline, reducing processing latency.}
    \item \techStack{Spring Boot, Docker, RabbitMQ, REST API, PostgreSQL, AOP.}
  \end{projectBlock}

  \begin{projectBlock}{Customer Relationship Management (CRM)}{Real-time call-center integration platform}
    \resumeItem{Integrated Socket.io for real-time customer data pop-ups triggered on incoming calls via Asterisk VoIP.}
    \resumeItem{Built missed-call log aggregation and inbound/outbound call status tracking in collaboration with the FE team.}
    \item \techStack{Spring Boot, Docker, RabbitMQ, REST API, MariaDB, Socket.io, JavaScript, Asterisk.}
  \end{projectBlock}

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Nong Lam University Ho Chi Minh City}{2018 -- 2022}
    {Bachelor of Information Technology}{Ho Chi Minh, Vietnam}
  \resumeItemListStart
    \resumeItem{Studied core Computer Science foundations: data structures, algorithms, OOP, and software engineering principles.}
    \resumeItem{Built strong communication, teamwork, and technical presentation skills through group projects and seminars.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
