%-------------------------
% Resume in Latex
% Author : Tran Manh Tuong
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
% \usepackage[usenames,dvipsnames]{color}
\usepackage[dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

% \newcommand{\resumeSubheading}[4]{
%   \vspace{-2pt}\item
%     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       \textbf{#1} & #2 \\
%       \textit{\small#3} & \textit{\small #4} \\
%     \end{tabular*}\vspace{-7pt}
% }

% \newcommand{\resumeSubheading}[4]{
%   \vspace{-2pt}\item
%     \begin{tabular*}{0.97\textwidth}[t]{@{}p{0.66\textwidth}@{\extracolsep{\fill}}>{\raggedright\arraybackslash}p{0.40\textwidth}@{}}
%       \textbf{#1} & \small #2 \\
%       \textit{\small #3} & \textit{\small #4} \\
%     \end{tabular*}
%     \vspace{-4pt}
% }

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{@{}p{0.68\textwidth}@{\extracolsep{\fill}}>{\raggedright\arraybackslash}p{0.27\textwidth}@{}}
      \textbf{#1} & \hspace{6pt}\small #2 \\
      \textit{\small #3} & \hspace{6pt}\textit{\small #4} \\
    \end{tabular*}
    \vspace{-4pt}
}

% \newcommand{\resumeProjectHeading}[2]{
%     \item
%     \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
%       \small#1 & #2 \\
%     \end{tabular*}\vspace{-7pt}
% }

% \newcommand{\resumeProjectHeading}[2]{
%     \item
%     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       #1 & \small #2 \\
%     \end{tabular*}
%     \vspace{-5pt}
% }

% \newcommand{\resumeProjectHeading}[3]{
%     \item
%     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       \textbf{#1} & \small #2 \\
%       \small{\textit{\textcolor{black!99}{#3}}} & \\
%     \end{tabular*}
%     \vspace{-5pt}
% }

% \newcommand{\resumeProjectHeading}[3]{
%     \item
%     \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
%       \textbf{#1} & #2 \\
%       \textit{\textcolor{black!99}{#3}} & \\
%     \end{tabular*}
%     \vspace{-5pt}
% }

\newcommand{\resumeProjectHeading}[3]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{@{}l@{\extracolsep{\fill}}r@{}}
      \textbf{#1} & #2 \\
      \multicolumn{2}{@{}l@{}}{\small\textit{\textcolor{black}{#3}}} \\
    \end{tabular*}
    \vspace{-3pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}

%     \textbf{\Huge \scshape Tran Manh Tuong} \\ \vspace{1pt}
%     \small Backend Developer \\
%     \small +84 878 006 569 $|$ \href{mailto:tuongtran1345@gmail.com}{\underline{Mail}} $|$ 
%     \href{https://linkedin.com/in/tuong-tm}{\underline{LinkedIn}} $|$
%     Ho Chi Minh, Vietnam

    \textbf{\Huge \scshape Tran Manh Tuong} \\ \vspace{1pt}
    \small Backend Developer \\

    \small 
    \faPhone\ +84 878 006 569 \quad
    \faEnvelope\ \href{mailto:tuongtran1345@gmail.com}{\underline{tuongtran1345@gmail.com}} \quad
    \faLinkedin\ \href{https://linkedin.com/in/tuong-tm}{\underline{LinkedIn}} \quad
    \faMapMarker*\ Ho Chi Minh, Vietnam

\end{center}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {INDOVINA BANK}{May 2025 -- Present}
      {Core Banking Developer}{Ho Chi Minh, Vietnam}

    \resumeSubheading
      {IDEA PLACE VIETNAM}{Dec 2023 -- Jan 2025}
      {SAP Consultant}{Ho Chi Minh, Vietnam}

    \resumeSubheading
      {LCS Group (Leading in Consulting and Services)}{Oct 2022 -- Oct 2023}
      {Java Developer}{Ho Chi Minh, Vietnam}

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {Digital Banking}
          {May 2025 -- Present}
          {A platform for digital financial services, including transfers, payments, and account management.}
          \resumeItemListStart           
            \resumeItem{Designed and developed APIs for core banking transaction processing.}
            \resumeItem{Developed APIs and stored procedures for transfers, payments, and card transactions.} 
            \resumeItem{Implemented account lifecycle operations, including account opening, full/partial settlement, and auto-renewal.}
            \resumeItem{Worked with Core Banking databases, gaining strong understanding of data models and transaction flows.}
            \resumeItem{Optimized SQL queries through execution plan analysis and performance tuning.}
            \resumeItem{Built scheduled job workflows with callback mechanisms to synchronize data between Core Banking and external systems.}
            \resumeItem{Synchronized transaction statuses and delivered updates to applications and end users via APIs.}
            \resumeItem{Integrated Core Banking systems with external platforms such as BDSD and OTT.}
          \resumeItemListEnd

      \resumeProjectHeading
          {AMS (Application Management Services)}
          {Dec 2023 -- Jan 2025}
          {SAP application support and development, covering system operations, user management, and ABAP enhancements.}
          \resumeItemListStart
            \item[] {\small \textbf{SAP BASIS:}}
            \resumeItem{Working with Japanese clients as an SAP Consultant, supporting daily operations and system activities.}
            \resumeItem{Gaining knowledge of user management processes, including auditing user information to ensure compliance with job requirements across various environments.}
            \resumeItem{Experiencing in Transport Request management, including updating ChaRM statuses and importing TRs into production environments.}
            \resumeItem{Managing OSS, including opening and tracking OSS tickets.}
            \resumeItem{Performing audits after client copy or deletion.}
            % \vspace{3pt} % Khoảng cách nhỏ giữa hai phần
            \item[] {\small \textbf{ABAP Developer:}}
            \resumeItem{Having an understanding of ABAP coding standards, including naming conventions, report programming, and best practices.}
            \resumeItem{Applied BAPI in SAP programming to enhance functionality and automation.}
            \resumeItem{Create Basic (changes) design document for addon ABAP programs.}
          \resumeItemListEnd

      \resumeProjectHeading
          {ESign Portal (ESP)}
          {Oct 2022 -- Oct 2023}
          {ESP is a portal that offers signature verification services for individuals and businesses.}
          \resumeItemListStart
            \resumeItem{Directly receiving requirements from customers, analyzing designs, and discussing with the team on how to implement and optimize features.}
            \resumeItem{Implementing and optimizing signatures verification process.}
            \resumeItem{Applying Docker to deploy the project on the production server.}
            \resumeItem{Applying RabbitMQ to receive customer information, manage messages and protect the service from external threats.}
            \resumeItem{Implementing AOP to manage information about files transferred to other microservices.}
            \resumeItem{Tech stack: Spring Boot, Docker, RabbitMQ, RestAPI, PostgreSQL, AOP.}
          \resumeItemListEnd

      \resumeProjectHeading
          {Customer Relationship Management (CRM)}
          {Mar 2023 -- Oct 2023}
          {CRM helps agents manage customer data, departments, and call center operations.}
          \resumeItemListStart
            \resumeItem{Key member in designing and implementing a variety of processes.}
            \resumeItem{Designing a database that meets the project requirements.}
            \resumeItem{Applying Docker to deploy the project on the production server.}
            \resumeItem{Managing departments within the company, including oversight of product quantities.}
            \resumeItem{Implementing Socket.io to connect with the frontend for displaying pop-up customer information when receiving calls.}
            \resumeItem{Collaborating with FE developers and designers to manage a page of phone information: aggregating missed calls, the list of outgoing and incoming phone numbers (time, status, etc.).}
            \resumeItem{Tech stack: Spring Boot, Docker, RabbitMQ, RestAPI, MariaDB, Socket.io, Javascript, Asterisk.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \begin{itemize}[leftmargin=0.15in, label={$\bullet$}]
        \resumeItem{SAP Basis, SAP HANA, ABAP.}
        \resumeItem{Java (Java 8, Spring Boot, etc.), RestAPI, Linux, HTML, CSS, Javascript.}
        \resumeItem{Working with: Docker, RabbitMQ, Redis, Consul, Database (PostgreSQL, MySQL).}
        \resumeItem{Handling work-related tools: Git, Sourcetree, Dbeaver, Notepad++, IntelliJ IDEA.}
     \end{itemize}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Academic Background}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Nong Lam University Ho Chi Minh City}{2018 -- 2022}
      {Information Technology}{Ho Chi Minh, Vietnam}
      \resumeItemListStart
        \resumeItem{Gained foundational knowledge of programming, data structures, OOP, and software engineering.}
        \resumeItem{Developed soft skills: communication, teamwork, and presentation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}