%-------------------------
% Resume in Latex - Final Professional Version
% Author: Tran Manh Tuong
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\small #1} & \small #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[3]{
    \item
    \begin{tabular*}{0.97\textwidth}[t]{@{}l@{\extracolsep{\fill}}r@{}}
      \textbf{#1} & \small #2 \\
      \multicolumn{2}{@{}l@{}}{\small\textit{\textcolor{black}{#3}}} \\
    \end{tabular*}
    \vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.25in, topsep=0pt, parsep=0pt, partopsep=0pt, itemsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Tran Manh Tuong} \\ \vspace{5pt}
    \small \faBriefcase\ Backend Developer \\ \vspace{3pt}
    \small 
    \faPhone\ +84 77 568 2978 \quad | \quad 
    \faEnvelope\ \href{mailto:tuongtran1345@gmail.com}{tuongtran1345@gmail.com} \quad | \quad 
    \faLinkedin\ \href{https://linkedin.com/in/tuong-tm}{LinkedIn} \quad | \quad 
    \faMapMarker*\ Ho Chi Minh, Vietnam
\end{center}

%-----------SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Banking:}{ Core Banking Systems, CASA, Loan Lifecycle.} \\
     \textbf{SAP:}{ SAP Basis, SAP HANA, ABAP, ChaRM, OSS Management.} \\
     \textbf{Languages/Frameworks:}{ Java (8/11/17), Spring Boot, REST API, PL/SQL, JavaScript.} \\
     \textbf{Cloud/DevOps:}{ Linux, Docker, RabbitMQ, Redis, Consul, Microservices, Asterisk.} \\
     \textbf{Databases:}{ Oracle (Core Banking), PostgreSQL, MySQL, MariaDB.} \\
     \textbf{Tools:}{ Git, IntelliJ IDEA, Eclipse, DBeaver, Postman, VSCode.}
    }}
 \end{itemize}

%-----------WORK EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {INDOVINA BANK}{May 2025 -- Present}
      {IT - SOFTWARE ENGINEER (CORE BANKING)}{Ho Chi Minh, Vietnam}
      \resumeItemListStart
        \resumeItem{Gained hands-on experience in core banking systems, with a strong understanding of Current Accounts, CASA, and end-to-end Loan Lifecycle workflows.}
        \resumeItem{Designed and developed RESTful APIs for processing core banking transactions, ensuring high data consistency and security.}
        \resumeItem{Gained deep expertise in Core Banking data models and transaction flows to design scalable database schemas.}
        \resumeItem{Developed complex Stored Procedures and automated jobs for critical banking operations: account opening, settlement, and auto-renewal.}
        \resumeItem{Built robust synchronization workflows between Core Banking and external OTT platforms, ensuring seamless transaction status updates via APIs.}
      \resumeItemListEnd

    \resumeSubheading
      {IDEA PLACE VIETNAM}{Dec 2023 -- Jan 2025}
      {SAP Consultant}{Ho Chi Minh, Vietnam}
      \resumeItemListStart
        \resumeItem{Working with Japanese clients, supporting daily SAP operations and user management.}
        \resumeItem{Managed Transport Requests (TRs) and updated ChaRM statuses in PROD environments.}
        \resumeItem{Developed ABAP enhancements and created design documents for addon programs.}
      \resumeItemListEnd

    \resumeSubheading
      {LCS GROUP}{Oct 2022 -- Oct 2023}
      {Java Developer}{Ho Chi Minh, Vietnam}
      \resumeItemListStart
        \resumeItem{Developed ESign Portal and CRM systems using Spring Boot and PostgreSQL, focusing on secure document handling.}
        \resumeItem{Gained deep expertise in Cryptography, including symmetric/asymmetric encryption (AES, RSA) and decryption processes for sensitive data protection.}
        \resumeItem{Implemented and managed various Digital Signature standards (XMLDSig, CMS/PKCS\#7) and PKI (Public Key Infrastructure) workflows.}
        \resumeItem{Integrated RabbitMQ for asynchronous message queuing and utilized Docker for consistent containerized deployments.}
        \resumeItem{Applied Aspect-Oriented Programming (AOP) to streamline logging and file transfer monitoring across microservices.}
      \resumeItemListEnd

    % \resumeSubheading
    %   {LCS GROUP}{Oct 2022 -- Oct 2023}
    %   {Java Developer}{Ho Chi Minh, Vietnam}
    %   \resumeItemListStart
    %     \resumeItem{Developed ESign Portal and CRM systems using Spring Boot, PostgreSQL, and RabbitMQ, focusing on robust security layers for sensitive document management.}
    %     \resumeItem{Mastered cryptographic workflows (AES, RSA) and Digital Signature standards (XMLDSig, CMS/PKCS\#7) within PKI frameworks to ensure end-to-end data protection.}
    %     \resumeItem{Utilized Docker for containerized deployment and applied AOP to streamline logging and file transfer monitoring across microservices architecture.}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Key Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {Digital Banking Platform}
          {May 2025 -- Present}
          {Core system for transfers, payments, and account management}
          \resumeItemListStart           
            \resumeItem{Built scheduled job workflows to synchronize data between Core Banking and external OTT systems.}
            \resumeItem{Ensured transaction integrity and delivered real-time updates via REST APIs.}
          \resumeItemListEnd
      
      \resumeProjectHeading
          {ESign Portal (ESP)}
          {Oct 2022 -- Oct 2023}
          {Signature verification services for individuals and businesses}
          \resumeItemListStart
            \resumeItem{Implemented AOP for tracking data transfers across microservices architecture.}
            \resumeItem{Analyzed requirements and optimized signature verification workflows.}
          \resumeItemListEnd    

      \resumeProjectHeading
          {Customer Relationship Management (CRM)}
          {Mar 2023 -- Oct 2023}
          {Omnichannel CRM for call center operations and data management}
          \resumeItemListStart
            \resumeItem{Implemented Socket.io for real-time customer data pop-ups during incoming calls.}
            \resumeItem{Collaborated with FE team to aggregate missed call logs and incoming/outgoing call status tracking.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Nong Lam University Ho Chi Minh City}{2018 -- 2022}
      {Bachelor of Information Technology}{Ho Chi Minh, Vietnam}
      \resumeItemListStart
        \resumeItem{Gained foundational knowledge of programming, data structures, OOP, and software engineering.}
        \resumeItem{Developed soft skills: communication, teamwork, and presentation.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\end{document}